### 2016-02-25 ch02-qlogms/excitation-design.tex
Some changse to CH02

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.

@@

 \subsection{A second order system}
Consider the second order system
\begin{align}
y(t) &= G(s,\theta) u(t) = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u(t),
\label{eq:excitation:2ndOrderSys}
\end{align}
with parameters $\theta=[\wn\;\damping]^{\T}$. 
The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$ and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.

When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in the amplitude of the transfer function~\citep{Oppenheim1983}:
  \begin{align}
   \left| G\left(\wM \right) \right| & \isdef
          \max_{\omega} \left| G\left( \omega \right)  \right|
        = \frac{\dc}
               {2 \damping \sqrt{1-\damping^2}}
               \label{eq:excitation:peakAmplitude}\\
   \wM &
        = \sqrt{1-2\damping^2} \wn
        \label{eq:excitation:peakFrequency}
    \text{.}
  \end{align}

@@

Consider the second-order subsystem with multiplicity $\multiplicity$:
\begin{equation}
  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{K} 
    &= 
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-K \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e. equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
\begin{assumption}

\end{assumption}

@@

  In this chapter, random-phase multisines are used since this is a reasonable choice for systems that are dominantly linear~\TODO{ref: BLA}.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
  \begin{itemize}
    \item the amplitude of the spectral lines $A_k$, and
    \item the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  \end{itemize}
  Note that the $k^{\text{th}}$ term in \eqref{eq:excitation:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.

@@

  \subsubsection{Exploiting the grid misalignment between the system and the grid}
  Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:excitation:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order system that shares the damping and \gls{DC} gain of the previous system but has a natural frequency $m\wn$.

  If one calculates their FRFs by evaluating \eqref{eq:excitation:secondOrderSystemCT}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
  Both FRFs share the same `shape', but are `located' at different frequencies.

@@

  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
  % Note that $\dc$ is a scaling factor for the FRF.
  % Hence the results for different values of $\dc$ only differ by a scaling factor.
  % So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.

@@

  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSystemCT}.

>>>>

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.

@@

 \subsection{A second order system}
Consider the second order system
\begin{align}
y(t) 
  &= 
  G(s,\theta) u(t) 
  = \frac{1}
                {\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}
      u(t),
\label{eq:excitation:2ndOrderSys}
\end{align}
with parameters $\theta=[\wn\;\damping]^{\T}$. 
The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$.

When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in the amplitude of the transfer function~\citep{Oppenheim1983}:
  \begin{align}
   \left| G\left(\wM \right) \right| & \isdef
          \max_{\omega} \left| G\left( \omega \right)  \right|
        = \frac{1}
               {2 \damping \sqrt{1-\damping^2}}
               \label{eq:excitation:peakAmplitude}\\
   \wM &
        = \sqrt{1-2\damping^2} \wn
        \label{eq:excitation:peakFrequency}
    \text{.}
  \end{align}
  The $3\unit{dB}$ bandwidth around this resonance peak is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.

@@

Consider the second-order subsystem with multiplicity $\multiplicity$:
\begin{equation}
  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\label{eq:excitation:secondOrderSubsystem}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{K} 
    &= 
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-K \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e. equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
\begin{assumption}
\TODO{assume separation in freq}
\end{assumption}

\begin{assumption}
\TODO{small damping}
\end{assumption}

\begin{remark}
\TODO{leads to block-diagonal information matrix such that the variance of the FRF is decoupled near the resonances}
\end{remark}

@@

  In this chapter, random-phase multisines are used since this is a reasonable choice for systems that are dominantly linear~\citep{Schoukens2004}.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
  \begin{itemize}
    \item the amplitude of the spectral lines $A_k$, and
    \item the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  \end{itemize}
  Note that the $k^{\text{th}}$ term in \eqref{eq:excitation:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.

@@

  \subsubsection{Exploiting the grid misalignment between the system and the grid}
  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order sub-system that shares the same parameters, except its natural frequency which is situated at $m\wn$.

  If one calculates their \glspl{FRF} by evaluating \eqref{eq:excitation:secondOrderSubsystem}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
  Both \glspl{FRF} share the same `shape', but are `located' at different frequencies.

@@

  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSubsystem}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
  % Note that $\dc$ is a scaling factor for the FRF.
  % Hence the results for different values of $\dc$ only differ by a scaling factor.
  % So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.

@@

  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSubsystem}.
